The pollination trade-off

### 2019-03-05 paper/manuscript.Rmd
Edits in the first subsection of the results. Now species names included in the manuscript are generated dynamically. Human readable lists are obtained using the  package

# species with both positive and negative relationships
get_sp_with_both_pos_neg <- . %>%
  dplyr::filter(effect_category != "neutral") %>%
  dplyr::group_by(plant_name) %>%
  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
  dplyr::filter(both)
sp_both_pos_neg <- facilitation_plot_df %>%
  get_sp_with_both_pos_neg()

@@

We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a). 
Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species, however, we also observed some important differences *within* species. 
For instance, `r numbers2words(nrow(sp_both_pos_neg))` of species sampled in multiple communities (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed evidence that facilitation (positive relationships) predominates in some communities while competition (negative relationships) predominates in others. 
Furthermore, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

@@

```{r facilitation-conspecific-stats}
drake::loadd(con_con_plot_df)
# overall counts of possitive/negative
sp_con_con <- con_con_plot_df %>%
  dplyr::group_by(effect_category) %>%
  dplyr::count() %>%
  dplyr::group_by() %>%
  dplyr::mutate(np = n/sum(n), 
                np = round_preserve_sum(np, 2)*100)
# species with contrasting behaviours
sp_con_both_pos_neg <- con_con_plot_df %>%
  get_sp_with_both_pos_neg()
```

Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with those that were closed. 
Here again, we found large differences between plants. 
Specifically, the difference was non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of plants, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open ($\alpha = 0.05$, Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c). 
Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (*H. incana* and *C. acanthoides*) had both significantly positive and negative differences.

>>>>

# species with both positive and negative relationships
get_sp_with_both_pos_neg <- . %>%
  dplyr::filter(effect_category != "neutral") %>%
  dplyr::group_by(plant_name) %>%
  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
  dplyr::filter(both)

# Get list of species with both positive and negative slopes
sp_both_pos_neg <- facilitation_plot_df %>%
  get_sp_with_both_pos_neg() %>%
  dplyr::mutate(plant_name = as.character(plant_name)) %>%
  dplyr::arrange(plant_name) %>%
  dplyr::mutate(plant_name = stringr::str_extract(plant_name,
                                                  "[A-Z]\\w+\\s[a-z]\\w+"), 
                plant_label = paste0("*", plant_name, "*")) 
# Human readable list of species with both positive and negative slopes
sp_both_pos_neg_names <- sp_both_pos_neg %$%
  glue::collapse(plant_label, sep = ", ", last = ", and ")

@@

We first examined the degree of facilitation/competition in natural communities. Specifically, we examined the slope of the relationship between the heterospecific and conspecific pollen deposited on stigmas of each species in a community. 
We found that overall neither facilitation nor competition dominates. 
Indeed, we found that the proportion of species that experienced a significantly positive or neggative relationship between heterospecific and conspecific pollen than neggative was very similar (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`%, respectively; Figure \@ref(fig:fig-trade-off-predictions)a). 
Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species; however, we also observed some important differences *within* species. 
For instance, `r numbers2words(nrow(sp_both_pos_neg))` of the species sampled across multiple communities (`r sp_both_pos_neg_names`) showed evidence that facilitation (positive relationships) predominated in some communities while competition (negative relationships) predominated in others. 
Interestingly, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen almost all plants had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

@@

```{r facilitation-conspecific-stats}
drake::loadd(con_con_plot_df)
# overall counts of possitive/negative
sp_con_con <- con_con_plot_df %>%
  dplyr::group_by(effect_category) %>%
  dplyr::count() %>%
  dplyr::group_by() %>%
  dplyr::mutate(np = n/sum(n), 
                np = round_preserve_sum(np, 2)*100)
# species with contrasting behaviours
sp_con_both_pos_neg <- con_con_plot_df %>%
  get_sp_with_both_pos_neg() %>%
  dplyr::arrange(plant_name) %>%
  dplyr::mutate(plant_label = dplyr::if_else(plant_name %in% sp_both_pos_neg$plant_name, shorten_sp_name(plant_name), plant_name),
                plant_label = paste0("*", plant_label, "*"))
```

Second, we compared the amount of conspecific pollen deposited on flowers that were open to animal-mediated pollinators with that of those that were closed. 
Here, we again found large differences between plants but with a clear tendency to find more pollen in open flowers. 
Specifically, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% of plants had significantly more pollen when open and `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open (the difference was non-signifcant for the remainding `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`%; Figure \@ref(fig:fig-trade-off-predictions)c). 
Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (`r glue::collapse(sp_con_both_pos_neg$plant_label, sep = ", ", last = ", and ")`) had both significantly positive and negative differences.
